The Sub-Millimetre User Reduction Facility: an iterative map-maker for SCUBA-2

### 2011-11-16 smurf_paper.tex
Filled in time-domain despiking section

>>>>

Spikes of short duration and high amplitude are often seen in the time
series data. If not removed, they can cause ringing in the FLT model
(Section~\ref{sec:flt}). Two alternative approaches may be used to remove
these spikes. This section describes the detection and removal of spikes
within the time series of each bolometer, and
section~\ref{sec:mapdespike} describes the detection and removal of
spikes within the final map. In practice, map-based despiking
(Section~\ref{sec:mapdespike}) usually gives superior results, and so
time-domain despiking is usually switched off.

\emph{Do we need some discussion of the physical causes and
characteristics of spikes?}

Each one-dimensional bolometer time series is processed independently. At
each time slice, the median value of the current bolometer in a box
centred on the time slice, and containing a specified number of time
slices (typically 50), is found. If the residual between the
time slice value and the median value is greater than some specified
multiple (typically 10) of the local noise level, the time slice is
flagged as a spike.

If the local noise level were estimated within the same box used to
determine the median value, a spike in the box would cause the local
noise level to be over-estimated severely. For this reason, the local
noise level is taken as the standard deviation of the values within a
neighbouring box on the ``down-stream'' side of the median box (that is,
the side that has already been checked for spikes). That is, the high end
of the noise box is just below the low end of the median filter box. This
introduces a slight asymmetry in the noise, but this should not matter
unless the noise varies significantly on a time scale shorter than the
box size.

This simple algorithm is not very good at distinguishing between spikes
and bright point sources, and so the threshold for spike detection is
usually raised when making maps of bright point sources.
